Imaging in MSK

### 2017-07-19 msk3-gift.rmd
updated gift

Info from [this presentation](https://meds.queensu.ca/central/assets/modules/msk_imaging/attach/imaging_slides.pdf).

>>>>

Info from [this presentation](https://meds.queensu.ca/central/assets/modules/msk_imaging/attach/imaging_slides.pdf). More up to date information on the *cost* of these modalities is available [here](https://www.treasury.gov.au/~/media/Treasury/Consultations%20and%20Reviews/Consultations/2016/2017%20PreBudget%20submissions/Submissions/PDF/Australian%20Diagnostic%20Imaging%20Association.ashx) however it was too hard to understand so just treat cost as qualitative.
